\documentclass{article}
\usepackage{amsthm}
\usepackage{parskip}
\newtheorem{thm}{Theorem}
\newtheorem{axiom}{Axiom}
\title{The (Motivations or Justifications) of that VARIK Dislikes Instant Messaging Services}
\author{la .varik.\ .VALefor.\ $<$varikvalefor@aol.com$>$}
\begin{document}
\maketitle

\section{Executive Summary}
For many instant messaging services $A$, that ($A$ is closed-source), that (VARIK dislikes the technical aspects of $A$), that ($A$ forbids that uses unofficial clients for $A$), that ($A$ is centralised), or that ($A$ demands that uses a telephone number) justifies that VARIK dislikes $A$.

VARIK dislikes Discord and Telegram and not likes XMPP.
\section{Discord}
\begin{thm}
	VARIK dislikes Discord.
\end{thm}
\begin{proof}
	${}$

	For all instant messaging services $A$, if ($A$ is closed-source and is imperfect) or ($A$ forbids that uses an unofficial client for $A$), then VARIK dislikes $A$.

	Discord is closed-source, is imperfect, and forbids that uses an unofficial client for Discord.

	Therefore, VARIK dislikes Discord.
\end{proof}

\section{Telegram}
\begin{thm}
	VARIK dislikes Telegram.
\end{thm}
\begin{proof}
	${}$

	For all instant messaging services $A$, if $A$ is centralised or demands that uses a telephone number, then VARIK dislikes $A$.

	Telegram is centralised and demands that uses a telephone number.

	Therefore, VARIK dislikes Telegram.
\end{proof}

\section{XMPP}
\begin{thm}
	VARIK not likes XMPP.
\end{thm}
\begin{proof}
	${}$

	For all instant messaging services $A$ which are protocols, if VARIK opines that the syntax of $A$ is clunky, then VARIK dislikes $A$.

	XMPP is an instant messaging service and is a protocol.

	VARIK opines that the syntax of XMPP is clunky.

	Therefore, VARIK dislikes XMPP.
\end{proof}
\end{document}
