\documentclass{article}

\usepackage{parskip}
\usepackage{hyperref}

\title{A Summary of the Religion of VARIK VALEFOR}
\author{la .varik. .VALefor.}

\begin{document}
\maketitle

\section{The Summary}
\subsection{The Abstract \{N\} or Whatever}
``Theistic Satanism'' is vague.  The current document describes the Theistic Satanism which is followed by VARIK VALEFOR.

\subsection{Practices/Morality}
VARIK's Theistic Satanism encourages/demands/whatever (loyalty to country), (grokking correct mathematics), cleverness/creativity, nonviolence, curiosity, humour, honesty, forgiveness, religious tolerance, non-xenophobia, non-arrogance, not demanding that anything is believed, and facilitating stuff which rocks.

\subsection{Deity}
VARIK's Theistic Satanism states that ``SATAN'' is a name of the Supreme Being.  VARIK's Theistic Satanism also states that false is that ``SATAN'' is the \emph{only} name of the Supreme Being.

VARIK uses ``God'' as a title of SATAN.

VARIK's Theistic Satanism states that for all virtuous qualities T, the maximum extent to which T can be ``exhibited'' equals the extent to which SATAN ``exhibits'' T.  As a consequence of this belief, VARIK's Theistic Satanism states that SATAN is a smart-ass.

\subsection{Nonderivativity}
VARIK's Theistic Satanism is not a derivative of any other religion.  Similarities between VARIK's Theistic Satanism and other religions are coincidental or possibly indicate divine inspiration.

\subsection{The Holy Book of the Religion of VARIK}
With the assistance of SATAN, VARIK maintains la ti'ocku, which is available at \href{http://git.varikvalefor.i2p/vvx/la-tihocku}{VARIK's Gitea instance} and \href{https://github.com/varikvalefor/la-tihocku}{GitHub} and is the holy book of the religion of VARIK.
\end{document}
