\documentclass{article}
\usepackage{amsthm}
\usepackage{parskip}
\usepackage[margin=1.25in]{geometry}
\newtheorem{thm}{Theorem}
\newtheorem{axiom}{Axiom}
\title{Reasons for Writing in the Third Person}
\author{Varik Valefor\\{\small $<$varikvalefor@aol.com$>$}}
\begin{document}
	\maketitle
	\section{Executive Summary}
		VARIK prefers writing in the third person over writing in the first
		person because\ldots
		\begin{itemize}
			\item VARIK dislikes pronouns, which can be avoided only by
				writing in the third person.
			\item VARIK finds that for all $j \in \left\{\textrm{first-person
				writing}, \textrm{second-person writing}\right\}$, the
				``tidiness'' of third-person writing is greater than the
				``tidiness'' of $j$.
			\item VARIK finds that the ease of writing in the third person is
				greater than the ease of writing in the first or second person.
		\end{itemize}
	\section{Lack of Pronouns}
		VARIK prefers writing in the third person over writing in the first
		and second person partially because when writing in the third
		person, VARIK can avoid using pronouns.

		Whereas first-person and second-person writing always contain
		pronouns, third-person writing need not contain pronouns.
		\subsection{Reasons for Necessity of Pronouns in First-Person and
		Second-Person Writing}
		\begin{thm}
			First-person writing always contains pronouns.
		\end{thm}
		\begin{proof}
			${}$

			First-person writing always contains variations of ``I'' or
			``we''.

			For all variations of ``I'' and ``we'', a variation is a pronoun.

			Therefore, first-person writing always contains pronouns.
		\end{proof}
		\begin{thm}
			Second-person writing always contains pronouns.
		\end{thm}
		\begin{proof}
			${ }$

			Second-person writing always contains variations of ``ye'' or
			``thou''.

			For all variations of ``ye'' and ``thou'' $g$, $g$ is a pronoun.

			Therefore, second-person writing always contains pronouns.
		\end{proof}
		\begin{axiom}
			The use of pronouns in third-person writing can always be avoided.
		\end{axiom}
	\section{Personal Preference}
		VARIK finds that the ease of writing in the third person is greater
		than the ease of writing in the first or second person.
		\subsection{Possible Reasons}
			\subsubsection{Writing Reports}
				To ensure that reports can be co-authored, VARIK has written
				reports in the third person since the early 2000s.  Because
				habits are built by doing things repeatedly, a habit of writing
				in the third person may have been built.
			\subsubsection{Preference for Mathematical Notation}
				\begin{thm}
					VARIK may have developed a habit of writing in the third
					person as a result of frequently writing in mathematical
					notation.
				\end{thm}
				\begin{proof}
					${ }$

					VARIK has frequently written things in mathematical notation
					for many years.

					Mathematical notation is always written in the third person.

					For all men $m$, for all actions $a$, $m$ may develop a habit
					of doing $a$ as a result of frequently doing $a$.

					Therefore, VARIK may have developed a habit of writing in
					mathematical notation as a result of frequently writing in
					mathematical notation.
				\end{proof}
\end{document}
